---
title: "workout01-mindy-dai"
author: "Mindy Dai"
date: "10/5/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2)
library(dplyr)
library(readr)
```

```{r}
nba <- read_csv("/Users/mindydai/hw-stat133/workout1/data/nba2018.csv", 
                col_names=TRUE)
nba$experience <- replace(nba$experience, nba$experience == 'R', 0)
nba$experience <- as.integer(nba$experience)
nba$salary <- nba$salary / 1000000
nba$position <- factor(nba$position)
levels(nba$position) <- c('center', 'power_fwd', 'point_guard', 
                  'small_fwd', 'shoot_guard')
nba <- mutate(nba, missed_fg = nba$field_goals_atts - nba$field_goals, missed_ft = nba$points1_atts - nba$points1, rebounds = nba$off_rebounds + nba$def_rebounds)
efficiency <- (nba$points + nba$rebounds + nba$assists + nba$steals + nba$blocks - nba$missed_fg - nba$missed_ft - nba$turnovers) / nba$games
nba <- mutate(nba, efficiency = efficiency)
```

```{r}
experience <- summarise(group_by(nba, team), experience = sum(experience))
salary <- summarise(group_by(nba, team), salary = sum(salary))
points3 <- summarise(group_by(nba, team), points3 = sum(points3))
points2 <- summarise(group_by(nba, team), points2 = sum(points2))
points1 <- summarise(group_by(nba, team), points1 = sum(points1))
points <- summarise(group_by(nba, team), points = sum(points))
off_rebounds <- summarise(group_by(nba, team), off_rebounds = sum(off_rebounds))
def_rebounds <- summarise(group_by(nba, team), def_rebounds = sum(def_rebounds))
assists <- summarise(group_by(nba, team), assists = sum(assists))
steals <- summarise(group_by(nba, team), steals = sum(steals))
blocks <- summarise(group_by(nba, team), blocks = sum(blocks))
turnovers <- summarise(group_by(nba, team), turnovers = sum(turnovers))
fouls <- summarise(group_by(nba, team), fouls = sum(fouls))
efficiency <- summarise(group_by(nba, team), efficiency = sum(efficiency))

teams <- merge(experience, salary, by.x='team', by.y='team')
teams <- merge(teams, points3, by.x='team', by.y='team')
teams <- merge(teams, points2, by.x='team', by.y='team')
teams <- merge(teams, points1, by.x='team', by.y='team')
teams <- merge(teams, points, by.x='team', by.y='team')
teams <- merge(teams, off_rebounds, by.x='team', by.y='team')
teams <- merge(teams, def_rebounds, by.x='team', by.y='team')
teams <- merge(teams, assists, by.x='team', by.y='team')
teams <- merge(teams, steals, by.x='team', by.y='team')
teams <- merge(teams, blocks, by.x='team', by.y='team')
teams <- merge(teams, turnovers, by.x='team', by.y='team')
teams <- merge(teams, fouls, by.x='team', by.y='team')
teams <- merge(teams, efficiency, by.x='team', by.y='team')
teams

```


```{r}
ggplot(data = teams, aes(x = reorder(team, salary), y = salary)) + geom_bar(stat='identity') +
  coord_flip() +
  ggtitle('NBA Teams ranked by Total Salary') +
  labs(x = 'Team', y = 'Salary (in millions)') +
  geom_hline(yintercept = mean(teams$salary), color = 'red')
```
```{r}
ggplot(data = teams, aes(x = reorder(team, points), y = points)) + geom_bar(stat='identity') +
  coord_flip() +
  ggtitle('NBA Teams ranked by Total Points') +
  labs(x = 'Team', y = 'Points') +
  geom_hline(yintercept = mean(teams$points), color = 'red')
```


```{r}
ggplot(data = teams, aes(x = reorder(team, efficiency), y = efficiency)) + geom_bar(stat='identity') +
  coord_flip() +
  ggtitle('NBA Teams ranked by Total Efficiency') +
  labs(x = 'Team', y = 'Efficiency') +
  geom_hline(yintercept = mean(teams$efficiency), color = 'red')
```

```{r}
ggplot(data = teams, aes(x = reorder(team, assists), y = assists)) + geom_bar(stat='identity') +
  coord_flip() +
  ggtitle('NBA Teams ranked by Total Assists') +
  labs(x = 'Team', y = 'Assists') +
  geom_hline(yintercept = mean(teams$assists), color = 'red')
```

I used assists as my index as I believe it is a good measure of team cohesiveness, which I think is very important to seeing how "good" a team is.

- Was this your first time working on a project with such file structure? If yes, how do you feel about it?
Yes, this was. I feel more educated on how to navigate my file system.

- Was this your first time using relative paths? If yes, can you tell why they are important for reproducibility purposes?
No, this was not my first time using relative paths. They are important as the names of directories leading up to your directory might change.

- Was this your first time using an R script? If yes, what do you think about just writing code (without markdown syntax)?
Yes, this was. I found it a bit weird as I had to check my console for the output, but I did get used to it.

- What things were hard, even though you saw them in class/lab?
Navigating my file system was a little bit hard.

- What was easy(-ish) even though we haven’t done it in class/lab?
Using "sink" was easy(-ish) as you just had to figure out the syntax.

- Did anyone help you completing the assignment? If so, who?
No.

- How much time did it take to complete this HW?
2 hours.

- What was the most time consuming part?
Figuring out how to make the plots.

- Was there anything interesting?
I thought using R Script instead of R Markdown was interesting.